Extending statistical models for source attribution of zoonotic diseases: A study of campylobacteriosis

### 2018-03-27 paper/finalish/article.tex
drop islandR package reference

All code for fitting the genotype distributions, estimating attribution probabilities and producing figures, along with the data are available in the R package `islandR` from \url{https://github.com/jmarshallnz/dirichlet_island}.

>>>>

All code for fitting the genotype distributions, estimating attribution probabilities and producing figures, along with the data are available from \url{https://github.com/jmarshallnz/dirichlet_island}.
